%-------------------------
% Resume in Latex
% Author : Hyunggi Chang, Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEmployment}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      {#5}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\
      \small{#2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeResearch}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} {\small #4 \vspace{-2pt}} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeTalk}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSkills}[1]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://changh95.github.io}{\Large Hyunggi Chang}} & Github: \href{https://github.com/changh95}{changh95} $|$ SlideShare: \href{https://www.slideshare.net/HyunggiChang/}{HyunggiChang} \\
  \href{https://www.cv-learn.com}{https://www.cv-learn.com} & Email : \href{mailto:hyunggi.chang95@gmail.com}{hyunggi.chang95@gmail.com} \\
  {} & Mobile : (+82) 010-2885-4493
\end{tabular*}

%-----------Summary-----------------
\section{Summary}
    \resumeSkills{I am interested in 3D computer vision and SLAM algorithms for mobile devices (VR/AR/Robotics). I have \\
    experiences on developing robust and safe perception algorithms for spatial AI system. To build an efficient and \\ 
    safe spatial AI system, I follow state-of-the-art algorithms and practise test-driven development.}

%-----------EXPERIENCE-----------------
\section{Employment}
  \resumeSubHeadingListStart
  
      \resumeSubheading
      {StradVision}{Seoul, South Korea}
      {Algorithm Engineer - Semantic SLAM (Full-time)}{Jun. 2021 - Present}
        \resumeItemListStart
            \resumeItem{Implement visual SLAM algorithms, using deep semantic features and road environment information.}
            \resumeItem{Verify performance and safety via auto-benchmark using continuous integration and development (CI/CD).}
            \resumeItem{Design modular software architecture, which complies with ASPICE and ISO 26262. }
        \resumeItemListEnd   
  
    \resumeSubheading
      {Virnect}{Seoul, South Korea}
      {Computer Vision Research Engineer / Manager (Full-time)}{Apr. 2019 - May 2021}
        \resumeItemListStart
            \resumeItem{Developed pose estimation and visual localization algorithms for mobile apps in the Perception \& ML team.}
            \resumeItem{Developed visual tracking software for a number of research projects in the Research Centre. }
            \resumeItem{Designed and built an automatic test \& benchmark system for continuous integration and development (CI/CD).}
        \resumeItemListEnd   
        
    \resumeSubheading
      {McKinsey \& Company}{London, UK}
      {Market Research (Part-time)}{Oct. 2017 - Dec. 2017}
      \resumeItemListStart
          \resumeItem{Performed market research in the AI \& Robotics market as the lead student researcher.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------Projects-----------------

\section{Projects}
  \resumeSubHeadingListStart
   \resumeProject
      {Vision-based auto valet parking system (Ongoing)}
      {Semantic mapping of parking lot and vehicle localization.}
           \resumeItemListStart
             \resumeItem{Simultaneous localization and mapping (SLAM) using multiple fisheye cameras.} 
             \resumeItem{Sensor fusion of semantic visual features (e.g. road markers) and wheel odometry.}
         \resumeItemListEnd
    \resumeProject
      {Mobile Augmented Reality SDK - Track SDK [\href{http://track.virnect.com}{\color{blue} LINK}]}
         {Cross-platform SDK for developing Augmented Reality (AR) applications.}
         \resumeItemListStart
             \resumeItem{Developed pose estimation and visual tracking algorithms, such as Image/QR/Model-based tracking and SLAM.} 
         \resumeItemListEnd
    \resumeProject
      {Easily Reconfigurable Marker-Based Tool Tracking Module}
    {Software module that enables easy object pose estimation on pen-shaped objects by using AR markers.}
    \resumeProject
      {Hyperspectral Wide-field Endoscopic Image Registration and Structure-from-Motion}
        {3D reconstruction of cancer that are invisible by eye, using multi-fibre hyperspectral endoscope.}
    \resumeProject
      {Mobile Rover for Environment Mapping and Survivor Detection in Disaster Scenarios}
      {Voice-controllable rover, using RGB-D SLAM, object detection, and collision-avoidance - 1st Prize winner in Hackathon.}
  \resumeSubHeadingListEnd

%-----------Skills-----------------

\section{Skills}
  \resumeSubHeadingListStart
    \resumeSkills{\textbf{Programming} - C17, C++17 (SSE/Neon), Python, Swift, Rust, MATLAB}
    \resumeSkills{\textbf{Vision/SLAM} - OpenCV, Eigen, TensorFlow, PyTorch, Ceres-solver}
    \resumeSkills{\textbf{Collaboration} - Git/GitHub, Docker, Linux, JIRA, TDD, Agile}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Imperial College London}{London, UK}
      {M.Res. Medical Robotics and Image-Guided Intervention (Merit)}{Oct. 2017 -- Sept. 2018}
      \resumeItemListStart
          \resumeItem{Course representative, Journal club lead}
      \resumeItemListEnd
    \resumeSubheading
      {University of Warwick}{Coventry, UK}
      {B.Eng. Manufacturing and Mechanical Engineering (Upper-Second Class Hons.)}{Oct. 2014 -- Jun. 2017}
      \resumeItemListStart
          \resumeItem{Course representative, University ambassador}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Research Experiences}
  \resumeSubHeadingListStart

    \resumeResearch
      {Cavendish Laboratory, University of Cambridge}{Cambridgeshire, UK}
      {Visiting Researcher (Advisor: Dr. Sarah Bohndiek)}{}{Jan. 2019 - Mar. 2019}
    \resumeResearch
      {Surgical Imaging and Biophotonics Laboratory, Imperial College London}{London, UK}
      {M.Res Student Researcher (Advisor: Prof. Daniel Elson)}{}{Jan. 2018 - Sept. 2018}
      \resumeResearch
      {HARMS Lab, Imperial College London}{London, UK}
      {M.Res Student Researcher (Advisor: Dr. George Mynolas)}{}{Oct. 2017 - Dec. 2017}
    \resumeResearch
      {Trace Metals in Medicine Laboratory, University of Warwick}{Coventry, UK}
      {B.Eng Student Researcher (Advisor: Dr. Joanna Collingwood)}{}{Oct. 2016 - Jun. 2017}
     \resumeResearch
      {International Institute for Product and Service Innovation, WMG}{Coventry, UK}
      {B.Eng Student Researcher (Advisor: Mr. Graeme Knowles)}{}{Oct. 2016 - Jun. 2017}
  \resumeSubHeadingListEnd

%-----------Talks-----------------
\section{Conference Talks}
    \resumeSubHeadingListStart
    
        \resumeTalk{MODUCON 2019}{2019}
            \resumeItemListStart
                \resumeItem{Evaluating customer-focused metrics for developing robust computer vision systems \href{https://youtu.be/ks96VTjAj6M}{\color{blue} [LINK]}}
            \resumeItemListEnd

        \resumeTalk{PyCon APAC 2019}{2019}
            \resumeItemListStart
                \resumeItem{Robot development with Python (Lightning talk) \href{https://youtu.be/Ym9vxOx5k8U}{\color{blue} [LINK]}}
            \resumeItemListEnd

        \resumeTalk{NVIDIA Jetson Meetup}{2019}
            \resumeItemListStart
                \resumeItem{NVIDIA Jetson Nano for intelligent robot development}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Community-----------------
\section{Community}
    \resumeSubHeadingListStart
        \resumeSubheading{Software Bootcamp Instructor}{2022 -- Present}
        {Grepp - \href{https://programmers.co.kr/learn/courses/13295}{\color{blue} ``Programmers Autonomous Driving Dev course"}}{}
    
        \resumeSubheading{Community Leader}{2019 -- Present}
        {Kakao community - \href{https://open.kakao.com/o/g8T5kxLb}{\color{blue} ``We will be SLAM Masters"}}{}
    
        \resumeSubheading{Tech Blog}{2019 -- Present}
            {Computer vision and SLAM blog - \href{https://www.cv-learn.com}{\color{blue} ``cv-learn blog"}}{}

        \resumeSubheading{Industry Seminar}{2019 -- Present}
        {Samsung, HANCOM Academy, HANCOM InSpace, J.MARPLE}{}
    
        \resumeSubheading{Charity Webinar}{2019 -- 2020}
        {Youtube webinar - \href{https://youtu.be/QKtyoNAdoqc}{\color{blue} ``A tutorial on object pose estimation"}, \href{https://youtu.be/eoLJMNJnTUg}{\color{blue} ``A tutorial on visual-SLAM"}}{}

        \resumeSubheading{Study Group Lead}{2019 -- 2020}
            {MODU Labs Group Study - \href{https://modulabs.co.kr/product/13th-wise-slam-study/}{\color{blue} ``Visual-SLAM"}, \href{https://tinyurl.com/65rbh23u}{\color{blue} ``Medical imaging"}}{}

        \resumeSubheading{Book Translation}{2018 -- 2019}
        {Community book translation: \href{https://changh95.github.io/20210123-slam-book-translation/}{\color{blue} ``Introduction to Visual-SLAM"}
        }{}
        
        
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
